---
title: |
  | \includegraphics[width=0.15\textwidth]{Crest.png}
  |
  |
  | Summative Assessment
  |
  | PO33Q: Determinants of Democracy --
  | Analysing Emergence, Survival, and Fall
author: "u1234567"
date: |
  \parbox{\textwidth}{
    \begin{center}
    Submitted on `r format(Sys.Date(), "%d %B, %Y")`\\[5em]
    \begin{tabular}{@{}l@{}}
    Word Count: XXX \\
    Word Count for Figures \& Tables: XXX \\
    Total Word Count: XXX
    \end{tabular}
    \end{center}
  }
output: 
  pdf_document:
    latex_engine: lualatex
    citation_package: biblatex
    toc: no
    number_sections: false
fontsize: 12pt
header-includes:  
  - \usepackage[style=apa,backend=biber,natbib=true]{biblatex} # sets the bib style
  - \addbibresource{referencesPO33Q.bib} # this is the .bib resource file
  - \renewcommand{\familydefault}{\sfdefault} # makes the font sans serif
  - \usepackage{booktabs} # for tables
  - \usepackage{tikz} # for the box on the cover page
  - \usetikzlibrary{calc} # for the box on the cover page
  - \usepackage{placeins} # set barriers within which figures are placed
  - \renewcommand{\contentsname}{Table of Contents} # Change toc title
  - \usepackage{tocloft}                            # For dotted leaders control
  - \renewcommand{\cftdotsep}{1}                    # Space between dots
  - \renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} # force dots for sections
  - \renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}    # …subsections
  - \renewcommand{\cftsubsubsecleader}{\cftdotfill{\cftdotsep}} # …subsubsections
  - \usepackage[HTML]{xcolor}
  - \definecolor{lightgray}{HTML}{e6e6e6} # choose grey for background
  - \pagecolor{lightgray}                 # set background color
  - \usepackage{setspace}  # allow onehalfspacing
  - \usepackage{needspace} # the remainder forces page breaks if
  - \usepackage{etoolbox}  # too little space remains after a (sub-)section heading
  - \preto{\section}{\par\Needspace*{7\baselineskip}}
  - \preto{\subsection}{\par\Needspace*{6\baselineskip}}
  - \preto{\subsubsection}{\par\Needspace*{5\baselineskip}}
---

\thispagestyle{empty}
```{=latex}
\begin{tikzpicture}[remember picture,overlay]
  \draw[line width=1pt]
    ($(current page.north west)+(18mm,-18mm)$) rectangle
    ($(current page.south east)+(-18mm,18mm)$);
\end{tikzpicture}
```
\vfill
\begin{center}
\includegraphics[width=0.25\textwidth]{Warwick.png}
\end{center}
\vspace{1cm}

\newpage

```{=latex}
\pagenumbering{roman}
\setcounter{tocdepth}{4}
\tableofcontents
```

\newpage

\listoffigures
\listoftables
\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\onehalfspacing


# Introduction

- State the puzzle and the resulting research question
- Outline the plan of the study
- State the main findings


# Literature Review & Theory

- Review the relevant literature
- You can cite something like this: \citep{prz:2000}
- Deduct the gap you are filling
- Explain the causal chain of your theory


# Hypotheses

- State the hypotheses you are testing:
  - H$_1$: 
  - H$_2$: 

# Conceptualisation & Measurement

- State the concepts
- Choose appropriate measures
- Feel free to present this in a table like Table \ref{tbl:conceptualisation} to supplement the text. But bear in mind that this adds to the word count proportional to the amount of space it occupies. This is why I have decreased the font size in the table itself. 

\FloatBarrier
\begin{table}[!h]
\fontsize{8}{10}\selectfont
\centering
\begin{tabular}{lll}
        &  \\[-1.8ex] \specialrule{.08em}{.05em}{.17em}\hline
        &  \\[-1.8ex]
Concept                 &  Attribute                        &   Variable                        \\

\hline
        &  \\[-1.2ex]

\multicolumn{2}{l}{\textbf{Dependent Variable}}     &                           \\

\addlinespace
Democracy       &   Participation     &   \citet{boix:2022}  \\
                &   Contestation      &                   \\

\addlinespace
\addlinespace

\multicolumn{2}{l}{\textbf{Independent Variables}}          &                           \\

\addlinespace
Economic Development  &     Wealth    & per capita GDP    \\
                      &     Growth    & per capita GDP growth \\
\addlinespace
Social Development    &     Health    & life expectancy at birth \\
                      &     Education & primary school enrolment \\
                      &     Urbanisation  & \% of population living in cities \\
\hline\specialrule{.08em}{.17em}{.05em}
& \\[-1.8ex] 
\end{tabular}
\caption{Conceptualisation and Mesasurement}
\label{tbl:conceptualisation}
\end{table}
\FloatBarrier


# Data & Methodology

- Outline the data used for analysis
- Explain the Markov Transition Model and why it is suitable for your analysis

# Analysis

- Test the hypotheses
- Explain what the results mean for the hypotheses
- Answer your research question
- You probably won't have to include a figure, but just in case, this is how it would work:

\FloatBarrier
```{r message=F, warning=F, echo=F, out.width='30%',fig.align='center',  fig.cap="\\label{fig:normal}Standard Normal Distribution"}
library(tidyverse)
x=seq(-3,3,length=200)
y=dnorm(x, mean = 0, sd = 1)

normaldata <- data.frame(x,y)

ggplot(normaldata, aes(x=x, y = y)) + 
  geom_density(stat="identity") +
  theme_classic() 
```
\FloatBarrier

As we can see in Figure \ref{fig:normal}...



# Discussion

- Discuss reasons why you have obtained your results
  - Why might coefficients be insignificant?
  - What alternative explanations are there?
- Relate your findings to the existing literature
 

# Conclusion

- State what the study has done
- State the main findings
- Answer your research question





\newpage

```{=latex}
\clearpage
\printbibliography[heading=bibintoc,title={List of References}]
\let\printbibliography\relax
```

\newpage

# Appendix {-}

```{r eval=FALSE}
# here goes all of your Rscript

x <- 1:10
mean(x)
```
