---
title: ""
output: 
  pdf_document:
    latex_engine: lualatex
    citation_package: biblatex
    toc: no
    number_sections: false
fontsize: 12pt
header-includes:    
  - \usepackage{graphicx}
  - |
    \newcommand*{\titleGM}{%
    \begingroup
    \thispagestyle{empty}
    {\centering\includegraphics[width=0.175\linewidth]{Crest.png}\\[3\baselineskip]}
    \hbox{%
      \hspace*{0.075\textwidth}%
      \rule{1.5pt}{0.6\textheight}%
      \hspace*{0.05\textwidth}%
      \parbox[b][0.6\textheight]{0.85\textwidth}{%
        \vspace{3\baselineskip} % <<< move text down relative to top of rule
        {\noindent\LARGE\bfseries PO33Q - Determinants of Democracy:\\Analysing Emergence, Survival, and Fall\\}\\[1\baselineskip]
        {\noindent\Large\bfseries Summative Assessment\\}\\[2\baselineskip]
        {\large \textit{\textbf{Warwick ID:} u1234567}}\\
        \vfill
        {\large Number of Words: XXXX}\\
        {\large Words for Figures and Tables: XXXX}\\
        {\large Total Number of Words: XXXX}\\[\baselineskip]
      }%
    }%
    \vfill
    \hfill \includegraphics[width=0.25\textwidth]{Warwick.png}
    \endgroup}
  - \usepackage[style=apa,backend=biber,natbib=true]{biblatex} # sets the bib style
  - \addbibresource{referencesPO33Q.bib} # this is the .bib resource file
  - \renewcommand{\familydefault}{\sfdefault} # makes the font sans serif
  - \usepackage{booktabs} # for tables
  - \usepackage{tikz} # for the box on the cover page
  - \usetikzlibrary{calc} # for the box on the cover page
  - \usepackage{placeins} # set barriers within which figures are placed
  - \renewcommand{\contentsname}{Table of Contents} # Change toc title
  - \usepackage{tocloft}                            # For dotted leaders control
  - \renewcommand{\cftdotsep}{1}                    # Space between dots
  - \renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} # force dots for sections
  - \renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}    # …subsections
  - \renewcommand{\cftsubsubsecleader}{\cftdotfill{\cftdotsep}} # …subsubsections
  - \PassOptionsToPackage{table}{xcolor}  # xcolor for setting grey background
  - \definecolor{lightgray}{HTML}{f0f0f0} # choose grey for background
  - \pagecolor{lightgray}                 # set background color
  - \usepackage{makecell}  # allow line breaks in modelsummary
  - \usepackage{setspace}  # allow onehalfspacing
  - \usepackage{needspace} # the remainder forces page breaks if
  - \usepackage{etoolbox}  # too little space remains after a (sub-)section heading
  - \preto{\section}{\par\Needspace*{7\baselineskip}}
  - \preto{\subsection}{\par\Needspace*{6\baselineskip}}
  - \preto{\subsubsection}{\par\Needspace*{5\baselineskip}}
---

```{r setup, include=FALSE}
# global options for code chunks
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, collapse = TRUE)

# control the placing of captions and resizing
options("tinytable_theme_placement_latex_float" = "H",
        tinytable_theme_resize_direction = "both")
```

```{=latex}
\DefTblrTemplate{firsthead,middlehead,lasthead}{default}{}
\DefTblrTemplate{firstfoot,middlefoot}{default}{}
\DefTblrTemplate{lastfoot}{default}% 
{
  \UseTblrTemplate{note}{default}
  \UseTblrTemplate{caption}{default}
}
```


\thispagestyle{empty}

```{=latex}
\titleGM
\clearpage
```

\newpage

```{=latex}
\pagenumbering{roman}
\setcounter{tocdepth}{4}
\tableofcontents
```

\newpage

\listoffigures
\listoftables
\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\onehalfspacing


# Introduction

- State the puzzle and the resulting research question
- Outline the plan of the study
- State the main findings


# Literature Review & Theory

- Review the relevant literature
- You can cite something like this: \citep{prz:2000}
- Deduct the gap you are filling
- Explain the causal chain of your theory


# Hypotheses

- State the hypotheses you are testing:
  - H$_1$: 
  - H$_2$: 

# Conceptualisation & Measurement

- State the concepts
- Choose appropriate measures
- Feel free to present this in a table like Table \ref{tbl:conceptualisation} to supplement the text. But bear in mind that this adds to the word count proportional to the amount of space it occupies. This is why I have decreased the font size in the table itself. 

\FloatBarrier
\begin{table}
\fontsize{8}{10}\selectfont
\centering
\begin{tabular}{lll}
        &  \\[-1.8ex] \specialrule{.08em}{.05em}{.17em}\hline
        &  \\[-1.8ex]
Concept                 &  Attribute                        &   Variable                        \\

\hline
        &  \\[-1.2ex]

\multicolumn{2}{l}{\textbf{Dependent Variable}}     &                           \\

\addlinespace
Democracy       &   Participation     &   \citet{boix:2022}  \\
                &   Contestation      &                   \\

\addlinespace
\addlinespace

\multicolumn{2}{l}{\textbf{Independent Variables}}          &                           \\

\addlinespace
Economic Development  &     Wealth    & per capita GDP    \\
                      &     Growth    & per capita GDP growth \\
\addlinespace
Social Development    &     Health    & life expectancy at birth \\
                      &     Education & primary school enrolment \\
                      &     Urbanisation  & \% of population living in cities \\
\hline\specialrule{.08em}{.17em}{.05em}
& \\[-1.8ex] 
\end{tabular}
\caption{Conceptualisation and Mesasurement}
\label{tbl:conceptualisation}
\end{table}
\FloatBarrier


# Data & Methodology

- Outline the data used for analysis
- Explain the Markov Transition Model and why it is suitable for your analysis
- In case you want to include the conditional probabilities:

Emergence:

\begin{equation}\label{eq:emergence}
P(y_{i,t} = 1 | y_{i, t-1} = 0)
\end{equation}
	
Survival:

\begin{equation}\label{eq:survival}
P(y_{i,t} = 1 | y_{i, t-1} = 1)
\end{equation}


To model democratic emergence we apply the conditional probability shown in Equation \ref{eq:emergence}...


# Analysis

- Test the hypotheses
- Explain what the results mean for the hypotheses
- Answer your research question
- You probably won't have to include a figure, but just in case, this is how it would work:

\FloatBarrier
```{r message=F, warning=F, echo=F, out.width='30%',fig.align='center',  fig.cap="\\label{fig:normal}Standard Normal Distribution"}
library(tidyverse)
x=seq(-3,3,length=200)
y=dnorm(x, mean = 0, sd = 1)

normaldata <- data.frame(x,y)

ggplot(normaldata, aes(x=x, y = y)) + 
  geom_density(stat="identity") +
  theme_classic() 
```
\FloatBarrier

As we can see in Figure \ref{fig:normal}...

Here is a \texttt{modesummary} example:

```{r}
# Load packages
library(modelsummary)
library(tinytable)
library(carData) # this is just a sample data set for illustration here

# Data
data("Prestige", package = "carData")

# Three regression models
m1 <- lm(prestige ~ education, data = Prestige)
m2 <- lm(prestige ~ income + type, data = Prestige)
m3 <- lm(prestige ~ education + income, data = Prestige)

# Create a list for models

models <- list(
  "(1)" = m1,
  "(2)" = m2,
  "(3)" = m3
)

# Coefficient map: named vector where names = original terms, values = display labels
cm <- c(
  "(Intercept)" = "Constant",
  "education"   = "Years of Education",
  "income"      = "Average Income"
)

# Create the modelsummary table
modelsummary(models, 
             title = 'Regression Models',
             gof_omit = 'DF|Deviance|Log.Lik|F|AIC|BIC|RMSE', 
             stars=TRUE,
             coef_map = cm)|>
  group_tt(j = list("\\makecell{Dependent Variable:\\\\Prestige Score for Occupation}" = 2:4))|> 
  theme_tt("resize", width = 0.5)|>  # resize the table as % of text width
  style_tt(tabularray_outer = "label={tab:regression}") # add label for cross ref

```

In Table \ref{tab:regression}, the coefficient for...



# Discussion

- Discuss reasons why you have obtained your results
  - Why might coefficients be insignificant?
  - What alternative explanations are there?
- Relate your findings to the existing literature
 

# Conclusion

- State what the study has done
- State the main findings
- Answer your research question





\newpage

```{=latex}
\clearpage
\printbibliography[heading=bibintoc,title={List of References}]
\let\printbibliography\relax
```

\newpage

```{=latex}
\appendix
\section{Appendix}
```

```{r echo=TRUE, eval=FALSE}
# here goes all of your Rscript

x <- 1:10
mean(x)
```
