---
title: |
  | \includegraphics[width=0.2\textwidth]{Crest.png}
  |
  |
  | Summative Assessment
  | PO33Q: Determinants of Democracy
subtitle: |
    |
    |
    | Word Count: XXX
    | Word Count for Figures: XXX
author: "u1234567"
date: 'Submitted on `r format(Sys.Date(), "%d %B, %Y")`'
output: 
  pdf_document:
    latex_engine: lualatex
    citation_package: biblatex
    toc: no
    number_sections: false
header-includes:  
  - \usepackage[style=apa,backend=biber,natbib=true]{biblatex}
  - \addbibresource{referencesPO33Q.bib}
  - \renewcommand{\familydefault}{\sfdefault} # makes the font sans serif
  - \usepackage{booktabs} # for tables
---

\thispagestyle{empty}
\vfill
\hfill \includegraphics[width=0.2\textwidth]{Warwick.png}

\newpage
```{=latex}
\pagenumbering{roman}
\setcounter{tocdepth}{4}
\tableofcontents
```

\newpage

\listoffigures
\listoftables
\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

# Introduction

# Literature Review / Theory

Text \citep{prz:2000}

# Hypotheses

# Conceptualisation and Measurement

\begin{table}[h]
\fontsize{8}{10}\selectfont
\centering
\begin{tabular}{lll}
        &  \\[-1.8ex] \toprule\hline
        &  \\[-1.8ex]
Concept                 &  Attribute                        &   Variable                        \\

\hline
        &  \\[-1.2ex]

\multicolumn{2}{l}{\textbf{Dependent Variable}}     &                           \\

\addlinespace
Democracy       &   Participation     &   \citep{boix:2022}  \\
                &   Contestation      &                   \\

\addlinespace
\addlinespace

\multicolumn{2}{l}{\textbf{Independent Variables}}          &                           \\

\addlinespace
Economic Development  &     Wealth    & per capita GDP    \\
                      &     Growth    & per capita GDP growth \\
\addlinespace
Social Development    &     Health    & life expectancy at birth \\
                      &     Education & primary school enrolment \\
                      &     Urbanisation  & \% of population living in cities \\
\hline\bottomrule
& \\[-1.8ex] 
\end{tabular}
\caption{Conceptualisation and Mesasurement}
\end{table}

# Data & Methodology

# Analysis

```{r message=F, warning=F, echo=F, out.width='30%',fig.align='center', fig.cap="\\label{fig:normal}Standard Normal Distribution"}
library(tidyverse)
x=seq(-3,3,length=200)
y=dnorm(x, mean = 0, sd = 1)

normaldata <- data.frame(x,y)

ggplot(normaldata, aes(x=x, y = y)) + 
  geom_density(stat="identity") +
  theme_classic() 
```

As we can see in Figure \ref{fig:normal}...

# Discussion



# Conclusion

\newpage

```{=latex}
\clearpage
\printbibliography[heading=bibintoc,title={List of References}]
\let\printbibliography\relax
```

\newpage

# Appendix I {.unnumbered}

```{r eval=FALSE}
# here goes all of your Rscript

x <- 1:10
mean(x)
```
